{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-09-20 documents/application.tex
Stuff and things

It is difficult to intuit how 40,000 watts can possibly be safe. It's useful to note, however, that the total energy dissipated in each pulse is . An oft-cited figure for the energy in a whisper is 10 mJ[wolframalpha]; and, while no clinical data are available, whispering into someone's chest is rarely considered calamitous.

@@

\clearpage
\printbibliography[heading=none, title={}, keyword={Flagship}]
\printbibliography[heading=none, title={}, keyword={standards}]

>>>>

It is difficult to intuit how 40,000 watts can possibly be safe. It's useful to note, however, that the total energy dissipated in each pulse is . An oft-cited figure for the energy in a whisper is 10 mJ[wolframalpha]; while no clinical data are available, whispering at someone is rarely considered calamitous!

Laser treatments can exceed hundreds of megawatts.

@@

\clearpage
\printbibliography[heading=none, title={}, keyword={standards}]

### 2020-09-20 documents/distribution.tex
Stuff and things

@@

Whether these values also explain the other datasets in \cite{Efficient2015}, such as the inactivation threshold vs frequency has not yet been determined.

@@

and here we have some dozen parameters. So these approximations should be regarded with great skepticism.

Since this entire covariance process will have to be repeated for SARS-NCoV-2 - that is, the CoV for NCoV, we have not bothered to fine-tune any of these fits; and so the idea that the Q-factor is higher than previously reported must still be regarded as only a speculative hypothesis.

T4 bacteriophage has far greater restraint, with only a 2.5\% $\pm \sigma$ variation in the icosahedral head dimensions \cite{Head1988}.\footnotemark

However, it offers a self-evident optimization: rather than applying a pulse of a single frequency, the pulses should be swept across the frequency distribution. From the (extremely crude) approximations on Inf. A above, this has little effect on $<$ 90-th percentile virions, but decreases the inactivation field of the last 10\% by perhaps 50 V/m.

In practice, not having a single frequency to design a microwave system around makes engineering quite a bit more complex; whether this tradeoff is worth making depends. "Broadbanding" makes all the $\lambda / 4$ structures behave rather poorly; depending on the bandwidth required, biasing may need to be made inductive or resistive.

>>>>

Charge \footnotemark

\footnotetext{
	It has been shown that, over decades, single species of viruses can effect large-scale changes in the net charges of their proteins without altering their function\cite{Dynamics2010}. Use of this technique will provide a selection bias towards immunity to electromagnetic fields. We do not have the biological knowledge to determine whether this is plausible; it simply seemed worth mentioning.

}

@@

We have not yet determined whether these values also explain the other datasets in \cite{Efficient2015}, such as the inactivation vs frequency plot.

T4 bacteriophage has far greater restraint, with only a 2.5\% $\pm \sigma$ variation in the dimensions of the icosahedral head \cite{Head1988}.\footnotemark

@@

and here we have some dozen parameters. So these approximations should be regarded with skepticism.

Since this entire covariance process will have to be repeated for SARS-NCoV \footnotemark we have not bothered to fine-tune any of these fits; and so the idea that the Q-factor is higher than previously reported must still be regarded as only a speculative hypothesis.

\footnotetext{...the CoV of NCoV}

This introduces a self-evident optimization: rather than applying a pulse of a single frequency, the pulses should be swept across the distribution. From the (extremely crude) approximations on Inf. A above, this has little effect on $<$ 90-th percentile virions, but decreases the inactivation field of the last 10\% by perhaps 50 V/m.

In practice, not having a single frequency to design a microwave system around makes the engineering quite a bit more difficult whether this tradeoff is worth making depends. "Broadbanding" makes all the $\lambda / 4$ structures behave rather poorly; depending on the bandwidth required, biasing may need to be made inductive or resistive.

### 2020-09-20 documents/paper.tex
Stuff and things

\begin{table} 
	\centering
	\begin{threeparttable}
		\caption{Safety limits from various standards}
		\begin{tabular}{lllll}
			\toprule
			Stubhead & \( df \) & \( f \) & \( \Wsqm \) & \( p \) \\
			\midrule
			&     \multicolumn{4}{c}{Spanning text}     \\
			Row 1    & 1        & 0.67    & 0.55       & 0.41    \\
			Row 2    & 2        & 0.02    & 0.01       & 0.39    \\
			Row 3    & 3        & 0.15    & 0.33       & 0.34    \\
			Row 4    & 4        & 1.00    & 0.76       & 0.54    \\
			\bottomrule
		\end{tabular}
		\begin{tablenotes}
			\small
			\item This is where authors provide additional information about
			the data, including whatever notes are needed.
		\end{tablenotes}
	\end{threeparttable}
\end{table}

@@

Unfortunately, the buried lede is that the power levels shown by [Yang 2015] are about twice the continuous safety levels.

@@

It has been shown that virions can effect large-scale changes in the electric charges of their \cite{Dynamics2010}.

Use of this technique will provide a selection bias towards immunity to electromagnetic fields, which could perhaps be effected by preferring extreme-sized mutants (shifting the resonance away from the applied field).

We do not have the biological knowledge to know if this is plausible; it simply seemed worth mentioning.

>>>>

%
%\begin{table} 
%	\centering
%	\begin{threeparttable}
%		\caption{Safety limits from various standards}
%		\begin{tabular}{lllll}
%			\toprule
%			Stubhead & \( df \) & \( f \) & \( \Wsqm \) & \( p \) \\
%			\midrule
%			&     \multicolumn{4}{c}{Spanning text}     \\
%			Row 1    & 1        & 0.67    & 0.55       & 0.41    \\
%			Row 2    & 2        & 0.02    & 0.01       & 0.39    \\
%			Row 3    & 3        & 0.15    & 0.33       & 0.34    \\
%			Row 4    & 4        & 1.00    & 0.76       & 0.54    \\
%			\bottomrule
%		\end{tabular}
%		\begin{tablenotes}
%			\small
%			\item This is where authors provide additional information about
%			the data, including whatever notes are needed.
%		\end{tablenotes}
%	\end{threeparttable}
%\end{table}

@@

and,

\begin{quote}
	 ...the two major groups that develop RF safety standards and
	guidelines (ICES and ICNIRP) agree that thermal effects continue to be the appropriate basis for protection
	against RF exposure at frequencies above 100 kHz.
\end{quote}

@@

### 2020-09-20 documents/personal_device.tex
Stuff and things

Trivially extending great work by \cite{Focusing}, a 40-element phased array using active-antenna techniques, each element of which consists of a negative-resistance device such as the BFP620 transistor, a tuning varactor, a patch antenna, and a resonator, each contributing a pulsed tone of 500 nanoseconds length and 10 milliwatts of RF power, and a focal point spatial scan rate and pulse repetition frequency of 6 KHz. produces a field pattern which, when scanned, appears to be suitable to deny respiratory transmission in a 'face shield' configuration.

Even point-blank, such a field would comply with all regulations by a factor of .

>>>>

Trivially extending great work by \cite{Focusing} on passive reflectarrays, a 40-element active-antenna phased array, each element of which consists of a negative-resistance device such as the BFP620 transistor, a tuning varactor, a patch antenna, and a resonator, each contributing a pulsed tone of 500 nanoseconds length and 10 milliwatts of RF power, and a focal point spatial scan rate and pulse repetition frequency of 6 KHz. produces a field pattern which, when scanned, appears to be suitable to deny respiratory transmission in a 'face shield' configuration.

Such a field would comply with all  standards by at least a factor of 20.

### 2020-09-20 documents/supplemental.tex
Stuff and things

\PRLsep{{\itshape Turbidimeter }}

@@

"Chromogenic" substances \cite{Fluorogenic1991}, or the degradation of various dyes like Methylene Blue.

@@

>>>>

\PRLsep{{\itshape Phage lysis sensing }}

@@

"Chromogenic" substances \cite{Fluorogenic1991}, or the degradation of various dyes like Methylene Blue; tetrazolium dye methods;

@@

The 0.8 uL sample in each was not sufficient to produce a measurable change in turbidity in a 0.2 uL - or we were not experienced enough to perform the phage lysis protocol properly.

However, we were not able to make smaller volumes of culture enter the log phase.
